---
title: "Data preperation part II of basal attributes article"
author: "Julius Fenn, Paul Sölder"
format:
  html:
    toc: true
    toc-depth: 3
    html-math-method: katex
    number-sections: true
---


# Notes


# global variables

Define your global variables (can take some time to run):

```{r}
#| label: global variables

save_CAMs_as_pictures = FALSE # TRUE = save CAMs as .json, .png files
```




# create raw data files



```{r}
#| label: create raw files
#| warning: false

# sets the directory of location of this script as the current directory
# setwd(dirname(rstudioapi::getSourceEditorContext()$path))

### load packages
# devtools::install_github('jdwilson4/multilayer_extraction')
require(pacman)
p_load('tidyverse', 'jsonlite', 'magrittr', 'xlsx',
       'stargazer', 'psych', 'jtools', 'DT', 'ggstatsplot', 
       'lavaan', 
       'regsem', 'MplusAutomation', 'igraph', 'shiny', 'ggplot2', 'tidyLPA', 'MultilayerExtraction',
       'Matrix', 'igraph', 'foreach', 'doParallel', 'parallel')
 

### list data files
setwd("data")
folders <- list.files(pattern = "^study_result.*")

### create data files
### get CAM data
writeLines("", "CAMdata.txt") # create file
text_connection <- file("CAMdata.txt", "a") # open connection to append

### get pre CAM data
writeLines("", "preCAM.txt") # create file
text_connection_pre <- file("preCAM.txt", "a") # open connection to append

### get post CAM data
writeLines("", "postCAM.txt") # create file
text_connection_post <- file("postCAM.txt", "a") # open connection to append

for(i in 1:length(folders)){
  setwd(folders[i])
  if(length(dir()) == 3){
    # print(i)
    ### CAM data
    setwd(dir()[2])
    tmp <- jsonlite::fromJSON(txt = "data.txt")
    writeLines(jsonlite::toJSON(x = tmp), text_connection)
    setwd("..")

    ### pre CAM data
    setwd(dir()[1])
    tmp <- jsonlite::fromJSON(txt = "data.txt")
    writeLines(jsonlite::toJSON(x = tmp), text_connection_pre)
    setwd("..")

    ### post CAM data
    setwd(dir()[3])
    tmp <- jsonlite::fromJSON(txt = "data.txt")
    writeLines(jsonlite::toJSON(x = tmp), text_connection_post)
    setwd("..")
  }
  setwd("..")
}

close(text_connection) # close connection CAM
close(text_connection_pre) # close connection
close(text_connection_post) # close connection

### move files to output folder
# copy files (not overwritten)
tmp_file_from <-  getwd()
setwd("../outputs/01_dataPreperation")
file.copy(from =  paste0(tmp_file_from, "/CAMdata.txt"), to = paste0(getwd(), "/CAMdata.txt"))
file.copy(from =  paste0(tmp_file_from, "/preCAM.txt"), to = paste0(getwd(), "/preCAM.txt"))
file.copy(from =  paste0(tmp_file_from, "/postCAM.txt"), to = paste0(getwd(), "/postCAM.txt"))

### remove files
file.remove(paste0(tmp_file_from, "/CAMdata.txt"))
file.remove(paste0(tmp_file_from, "/preCAM.txt"))
file.remove(paste0(tmp_file_from, "/postCAM.txt"))


### load functions
setwd("../../functions")
for(i in 1:length(dir())){
  # print(dir()[i])
  source(dir()[i], encoding = "utf-8")
}


setwd("../functions_CAMapp")
for(i in 1:length(dir())){
  # print(dir()[i])
  source(dir()[i], encoding = "utf-8")
}
rm(i)



### summary function
data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      se = sd(x[[col]], na.rm=TRUE) / sqrt(length(x[[col]])))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- plyr::rename(data_sum, c("mean" = varname))
  return(data_sum)
}
```


# set up data.frame questionnaires


```{r}
#| label: create questionnaires files
#| warning: false

setwd("outputs/01_dataPreperation")
# > pre study
suppressMessages(
  read_file('preCAM.txt') %>%
    # ... split it into lines ...
    str_split('\n') %>% first() %>%
    # ... filter empty rows ...
    discard(function(x)
      x == '') %>%
    discard(function(x)
      x == '\r') %>%
    # ... parse JSON into a data.frame
    map_dfr(fromJSON, flatten = TRUE)
) -> dat_preCAM
# > post CAM
read_file('postCAM.txt') %>%
  # ... split it into lines ...
  str_split('\n') %>% first() %>%
  # ... filter empty rows ...
  discard(function(x)
    x == '') %>%
  discard(function(x)
    x == '\r') -> tmp_postCAM


tmp_out <- list()
for (i in 1:length(tmp_postCAM)) {
  tmp_out[[i]] <- fromJSON(tmp_postCAM[i])
  tmp_out[[i]]$"21" <- NULL # causes error
}

dat_postCAM <- dplyr::bind_rows(tmp_out)
rm(tmp_postCAM)
rm(tmp_out)



### create counter variable for both data sets
# > pre study
dat_preCAM$ID <- NA

tmp_IDcounter <- 0
for (i in 1:nrow(dat_preCAM)) {
  if (!is.na(dat_preCAM$sender[i]) &&
      dat_preCAM$sender[i] == "Greetings") {
    # tmp <- dat_preCAM$prolific_pid[i]
    tmp_IDcounter = tmp_IDcounter + 1
  }
  dat_preCAM$ID[i] <- tmp_IDcounter
}

# > post CAM
dat_postCAM$ID <- NA

tmp_IDcounter <- 0
for (i in 1:nrow(dat_postCAM)) {
  if (!is.na(dat_postCAM$sender[i]) &&
      dat_postCAM$sender[i] == "CAMfeedbackGeneral") {
    # tmp <- dat_postCAM$prolific_pid[i]
    tmp_IDcounter = tmp_IDcounter + 1
  }
  dat_postCAM$ID[i] <- tmp_IDcounter
}



### keep only complete data sets
# > pre study
# sort(table(dat_preCAM$ID))
sum(table(dat_preCAM$ID) != max(table(dat_preCAM$ID)))
sum(table(dat_preCAM$ID) == max(table(dat_preCAM$ID)))

dat_preCAM <-
  dat_preCAM[dat_preCAM$ID %in% names(table(dat_preCAM$ID))[table(dat_preCAM$ID) == max(table(dat_preCAM$ID))], ]

# > post CAM
# sort(table(dat_postCAM$ID))
sum(table(dat_postCAM$ID) != max(table(dat_postCAM$ID)))
sum(table(dat_postCAM$ID) == max(table(dat_postCAM$ID)))


dat_postCAM <-
  dat_postCAM[dat_postCAM$ID %in% names(table(dat_postCAM$ID))[table(dat_postCAM$ID) == max(table(dat_postCAM$ID))], ]



### json (from JATOS) to 2D data.frame
# > pre study
# add paradata
tmp_notNumeric <-
  str_subset(string = colnames(dat_preCAM), pattern = "^meta|^R")
tmp_notNumeric <-
  str_subset(string = tmp_notNumeric,
             pattern = "labjs|location",
             negate = TRUE)

### get survey
vec_ques <- c("PROLIFIC_PID",
              "dummy_informedconsent",
              "commCheck",
              tmp_notNumeric)

vec_notNumeric = c("PROLIFIC_PID", tmp_notNumeric)

questionnaire_preCAM <- questionnairetype(
  dataset = dat_preCAM,
  listvars = vec_ques,
  notNumeric = vec_notNumeric,
  verbose = FALSE
)

dim(questionnaire_preCAM)



# > post CAM
tmp_numeric <-
  str_subset(string = colnames(dat_postCAM), pattern = "^nfc")


vec_ques <- c(
  "PROLIFIC_PID",
  "commCheck",
  "feedCAM_repres",
  "feedCAM_technicalprobs",
  "feedCAM_technicalprobsText",
  "feedCAM_already",
  "feedCAM_alreadyText",
  "openQuestion_MaterialSystem",
  "openQuestion_Ethic",
  "openQuestion_missedPositive",
  "openQuestion_missedNegative",
  "outcome_research",
  "outcome_prohibition",
  "outcome_buy",
  "outcome_buy_text",
  "education",
  "experienceMS",
  tmp_numeric,
  "feedback_critic"
)



vec_notNumeric = c(
  "PROLIFIC_PID",
  "feedCAM_technicalprobsText",
  "feedCAM_alreadyText",
  "openQuestion_MaterialSystem",
  "openQuestion_Ethic",
  "openQuestion_missedPositive",
  "openQuestion_missedNegative",
  "outcome_research",
  "outcome_prohibition",
  "outcome_buy",
  "outcome_buy_text",
  "education",
  "experienceMS",
  "feedback_critic"
)

questionnaire_postCAM <- questionnairetype(
  dataset = dat_postCAM,
  listvars = vec_ques,
  notNumeric = vec_notNumeric,
  verbose = FALSE
)

questionnaire_postCAM$feedback_critic[questionnaire_postCAM$feedback_critic == ""] <-
  NA
dim(questionnaire_postCAM)


questionnaire_postCAM$multipleEthic <- NA
tmp_multipleEthic <-
  cbind(dat_postCAM$ID, dat_postCAM$multipleEthic)

questionnaire_postCAM$multiplePositive <- NA
tmp_multiplePositive <-
  cbind(dat_postCAM$ID, dat_postCAM$multiplePositive)

questionnaire_postCAM$multipleNegative <- NA
tmp_multipleNegative <-
  cbind(dat_postCAM$ID, dat_postCAM$multipleNegative)


for (i in questionnaire_postCAM$ID) {
  # add multipleEthic
  tmp <- tmp_multipleEthic[tmp_multipleEthic[, 1] == i,]
  if (length(unlist(tmp[, 2])) == 3) {
    questionnaire_postCAM$multipleEthic[questionnaire_postCAM$ID == i] <-
      paste0(unlist(tmp[, 2]), collapse = " \\ ")
  }
  
  # add multiplePositive
  tmp <- tmp_multiplePositive[tmp_multiplePositive[, 1] == i,]
  if (length(unlist(tmp[, 2])) == 3) {
    questionnaire_postCAM$multiplePositive[questionnaire_postCAM$ID == i] <-
      paste0(unlist(tmp[, 2]), collapse = " \\ ")
  }
  
  # add multipleNegative
  tmp <- tmp_multipleNegative[tmp_multipleNegative[, 1] == i,]
  if (length(unlist(tmp[, 2])) == 3) {
    questionnaire_postCAM$multipleNegative[questionnaire_postCAM$ID == i] <-
      paste0(unlist(tmp[, 2]), collapse = " \\ ")
  }
}


dim(questionnaire_postCAM)



### merge all data sets
# remove one missing
questionnaire_preCAM <-
  questionnaire_preCAM[questionnaire_preCAM$PROLIFIC_PID %in% questionnaire_postCAM$PROLIFIC_PID,]


questionnaire_postCAM$ID <- NULL
questionnaire <-
  left_join(questionnaire_preCAM, questionnaire_postCAM, by = "PROLIFIC_PID")


## all missing answers to NA
questionnaire[questionnaire == ""] <- NA
## all feedback smaller than 3 characters to NA
questionnaire$feedback_critic[nchar(questionnaire$feedback_critic) <= 2] <-
  NA

dim(questionnaire)


### save files
## save as .xlsx file
xlsx::write.xlsx2(x = questionnaire, file = "questionnaire.xlsx")
## save as R object
saveRDS(questionnaire, file = "questionnaire.rds")
```

# get reaction times for single components

Plot time taken (in minutes) by participants for single components of study:

```{r, message = FALSE}
#| label: get reaction times by component

dat_duration <-
  data.frame(
    duration = NA,
    sender = NA,
    ID = NA,
    PROLIFIC_PID = NA
  )



for (i in 1:length(unique(dat_preCAM$ID))) {
  tmp_PID <-
    dat_preCAM$PROLIFIC_PID[dat_preCAM$ID ==  unique(dat_preCAM$ID)[i] &
                              !is.na(dat_preCAM$PROLIFIC_PID)]
  
  
  
  # pre CAM
  tmp_preCAM <-
    data.frame(duration = dat_preCAM$duration[dat_preCAM$ID == unique(dat_preCAM$ID)[i]] / 1000,
               sender = dat_preCAM$sender[dat_preCAM$ID == unique(dat_preCAM$ID)[i]])
  tmp_preCAM <- tmp_preCAM[!is.na(tmp_preCAM$sender), ]
  
  # post CAM
  tmp_postCAM <-
    data.frame(duration = dat_postCAM$duration[dat_postCAM$ID == unique(dat_postCAM$ID)[i]] / 1000,
               sender = dat_postCAM$sender[dat_postCAM$ID == unique(dat_postCAM$ID)[i]])
  tmp_postCAM <- tmp_postCAM[!is.na(tmp_postCAM$sender), ]
  
  
  tmp <- rbind(tmp_preCAM, tmp_postCAM)
  
  
  if (all(is.na(dat_duration))) {
    dat_duration <- data.frame(
      duration = tmp$duration,
      sender = tmp$sender,
      ID = rep(i, times = nrow(tmp)),
      PROLIFIC_PID = rep(tmp_PID, times = nrow(tmp))
    )
    
    
  } else{
    dat_duration <-
      rbind(
        dat_duration,
        data.frame(
          duration = tmp$duration,
          sender = tmp$sender,
          ID = rep(i, times =
                     nrow(tmp)),
          PROLIFIC_PID = rep(tmp_PID, times =
                               nrow(tmp))
        )
      )
  }
}

## remove empty sender
dat_duration <- dat_duration[!is.na(dat_duration$sender),]
dat_duration <- dat_duration[!is.na(dat_duration$duration),]

dat_duration$sender[dat_duration$sender == "done"] <-
  "CAM instructions"

## save as .xlsx
# write.xlsx2(x = dat_duration, file = "outputs/para_duration_singleComponents.xlsx")

#### plot
dat_duration$ID <- factor(dat_duration$ID)
p <- dat_duration %>%
  ggplot(aes(x = sender, y = duration, color = PROLIFIC_PID)) +
  geom_point() +
  geom_jitter(width = 0.15) +
  theme(axis.text.x = element_text(angle = 90)) + theme(legend.position =
                                                          "none")
p

## save ggplot as PDF
ggsave(filename = "outputs/01_dataPreperation/durations_components.pdf", p)


# Calculate the mean duration in seconds for each sender and sort by mean duration
tmp <- dat_duration %>%
  group_by(sender) %>%
  summarise(N = n(),
            mean_duration = mean(duration, na.rm = TRUE)) %>%
  arrange(desc(mean_duration))
DT::datatable(tmp, options = list(pageLength = 5)) 
```


## set up CAM data

Load CAM data

```{r, message = FALSE}
#| label: get raw CAM data pre

setwd("outputs/01_dataPreperation")
suppressMessages(read_file("CAMdata.txt") %>%
  # ... split it into lines ...
  str_split('\n') %>% first() %>%
    discard(function(x) x == '') %>%
    discard(function(x) x == '\r') %>%
  # ... filter empty rows ...
  discard(function(x) x == '')) -> dat_CAM_pre

raw_CAM <- list()
for(i in 1:length(dat_CAM_pre)){
  raw_CAM[[i]] <- jsonlite::fromJSON(txt = dat_CAM_pre[[i]])
}
```

Create CAM files, draw CAMs and compute network indicators

```{r, message = FALSE}
#| label: draw CAMs, network indicators, wordlist

### create CAM single files (nodes, connectors, merged)
CAMfiles <- create_CAMfiles(datCAM = raw_CAM, reDeleted = TRUE)


# remove testing data sets
CAMfiles[[1]] <- CAMfiles[[1]][CAMfiles[[1]]$participantCAM %in% questionnaire$PROLIFIC_PID,]
CAMfiles[[2]] <- CAMfiles[[2]][CAMfiles[[2]]$participantCAM %in% questionnaire$PROLIFIC_PID,]
CAMfiles[[3]] <- CAMfiles[[3]][CAMfiles[[3]]$participantCAM.x %in% questionnaire$PROLIFIC_PID,]

### draw CAMs
CAMdrawn <- draw_CAM(dat_merged = CAMfiles[[3]],
                     dat_nodes = CAMfiles[[1]],ids_CAMs = "all",
                     plot_CAM = FALSE,
                     useCoordinates = TRUE,
                     relvertexsize = 3,
                     reledgesize = 1)

### network indicators
tmp_microIndicator <- V(CAMdrawn[[1]])$label
networkIndicators <- compute_indicatorsCAM(drawn_CAM = CAMdrawn, 
                                           micro_degree = tmp_microIndicator, 
                                           micro_valence = tmp_microIndicator, 
                                           micro_centr_clo = tmp_microIndicator, 
                                           micro_transitivity = tmp_microIndicator, 
                                           largestClique = FALSE)


### wordlist
CAMwordlist <- create_wordlist(
  dat_nodes =  CAMfiles[[1]],
  dat_merged =  CAMfiles[[3]],
  useSummarized = TRUE,
  order = "frequency",
  splitByValence = FALSE,
  comments = TRUE,
  raterSubsetWords = NULL,
  rater = FALSE
)

DT::datatable(CAMwordlist, options = list(pageLength = 5))
```






### plot CAMs using igraph package

Just plot first 10 CAMs for an impression

```{r}
#| label: draw first 10 CAMs

for(i in 1:10){ # length(CAMdrawn)
  plot(CAMdrawn[[i]], edge.arrow.size = .7,
       layout=layout_nicely, vertex.frame.color="black", asp = .5, margin = -0.1,
       vertex.size = 10, vertex.label.cex = .9)
}
```




### save CAMs as .json files, and as .png (igraph)


```{r, message = FALSE}
#| label: save CAM pictures

if(save_CAMs_as_pictures){
setwd("outputs/01_dataPreperation")

setwd("savedCAMs")
setwd("png")
### remove all files if there are any
if(length(list.files()) >= 1){
  file.remove(list.files())
  cat('\n!
      all former .png files have been deleted')
}

### if no participant ID was provided replace by randomly generated CAM ID
if(all(CAMfiles[[3]]$participantCAM.x == "noID")){
  CAMfiles[[3]]$participantCAM.x <- CAMfiles[[3]]$CAM.x
}

### save as .json files, and as .png (igraph)
ids_CAMs <- unique(CAMfiles[[3]]$participantCAM.x); length(ids_CAMs)


for(i in 1:length(ids_CAMs)){
  save_graphic(filename = paste0("CAM", ids_CAMs[i])) #  paste0(ids_CAMs[i]))
  CAM_igraph <- CAMdrawn[[c(1:length(CAMdrawn))[
    names(CAMdrawn) == paste0(unique(CAMfiles[[3]]$participantCAM.x)[i])]]]
  plot(CAM_igraph, edge.arrow.size = .7,
       layout=layout_nicely, vertex.frame.color="black", asp = .5, margin = -0.1,
       vertex.size = 10, vertex.label.cex = .9)
  dev.off()
}

setwd("../json")
### remove all files if there are any
if(length(list.files()) >= 1){
  file.remove(list.files())
  cat('\n!
      all former .json files have been deleted')
}
for(i in 1:length(raw_CAM)){
  if(!is_empty(raw_CAM[[i]]$nodes)){
    if(nrow(raw_CAM[[i]]$nodes) > 5){
      if(raw_CAM[[i]]$creator %in% questionnaire$PROLIFIC_PID){ # only if not deleted previously
              write(toJSON(raw_CAM[[i]], encoding = "UTF-8"),
            paste0(raw_CAM[[i]]$creator, ".json"))
      }
    }
  }
}
}
```



### delete CAMs with star topology and no inter-connections

```{r}
#| label: delete CAMs

### 10% of participants have connected all basal attributes to the central one
barplot(
  table(
    networkIndicators$degreetot_micro_AkzeptanzeinesneuenMaterialsystems
  ) / nrow(networkIndicators)
)

### delete extreme CAMs without any inter-connections between basal attributes
vec_delete <- c()
h = 1

for (i in 1:nrow(networkIndicators)) {
  if (networkIndicators$degreetot_micro_AkzeptanzeinesneuenMaterialsystems[i] == 32 &
      networkIndicators$transitivity_macro[i] == 0) {
    vec_delete[h] <- names(CAMdrawn)[i]
    h = h + 1
    
    plot(
      CAMdrawn[[i]],
      edge.arrow.size = .7,
      layout = layout_nicely,
      vertex.frame.color = "black",
      asp = .5,
      margin = -0.1,
      vertex.size = 10,
      vertex.label.cex = .9,
      main = networkIndicators$CAM_ID[i]
    )
  }
}

if (length(vec_delete) > 1) {
  cat(length(vec_delete), "CAMs are removed from the data set")
  
  ## remove deleted CAMs from
  
  #> CAM files
  CAMfiles_clean <- CAMfiles
  CAMfiles_clean[[1]] <-
    CAMfiles_clean[[1]][!CAMfiles_clean[[1]]$participantCAM %in% vec_delete,]
  CAMfiles_clean[[2]] <-
    CAMfiles_clean[[2]][!CAMfiles_clean[[2]]$participantCAM %in% vec_delete,]
  CAMfiles_clean[[3]] <-
    CAMfiles_clean[[3]][!CAMfiles_clean[[3]]$participantCAM.x %in% vec_delete,]
  
  #> drawn CAMs
  CAMdrawn_clean <- CAMdrawn[!names(CAMdrawn) %in% vec_delete]
  
  #> network indicators
  networkIndicators_clean <-
    networkIndicators[!networkIndicators$participantCAM %in% vec_delete,]

  #> re-create wordlist
  CAMwordlist_clean <- create_wordlist(
    dat_nodes =  CAMfiles_clean[[1]],
    dat_merged =  CAMfiles_clean[[3]],
    useSummarized = TRUE,
    order = "frequency",
    splitByValence = FALSE,
    comments = TRUE,
    raterSubsetWords = NULL,
    rater = FALSE
  )
  
  
    #> questionnaire
  questionnaire_clean <-
    questionnaire[!questionnaire$PROLIFIC_PID %in% vec_delete,]
  
}
```





## save all final files

```{r}
#| label: save final files

setwd("outputs/01_dataPreperation/final")

if (length(vec_delete) > 1) {
  if (all(questionnaire_clean$PROLIFIC_PID == networkIndicators_clean$participantCAM) &
      all(questionnaire_clean$PROLIFIC_PID == unique(CAMfiles_clean[[1]]$participantCAM))) {
    # save questionnaire
    ## save as .xlsx file
    xlsx::write.xlsx2(x = questionnaire_clean, file = "questionnaire.xlsx")
    ## save as R object
    saveRDS(questionnaire_clean, file = "questionnaire.rds")
    
    
    # save network indicators combined and clean
    ## save as .xlsx file
    xlsx::write.xlsx2(x = networkIndicators_clean, file = "networkIndicators.xlsx")
    ## save as R object
    saveRDS(networkIndicators_clean, file = "networkIndicators.rds")
    
    # save CAMfiles
    ## save as R object
    saveRDS(CAMfiles_clean, file = "CAMfiles.rds")
    
    # save drawn CAMs
    ## save as R object
    saveRDS(CAMdrawn_clean, file = "CAMdrawn.rds")
    
    # save wordlist
    ## save as .xlsx file
    xlsx::write.xlsx2(x = CAMwordlist_clean, file = "CAMwordlist.xlsx")
    
    cat("clean data sets have been sucessfully saved")
  }
}
```
