---
title: "Main File for part II of basal attributes article"
author: "Julius Fenn"
format:
  html:
    toc: true
    toc-depth: 3
    html-math-method: katex
---

```{r}
#| echo: false
#| warning: false
#| results: hide

# sets the directory of location of this script as the current directory
# setwd(dirname(rstudioapi::getSourceEditorContext()$path))

########################################
# load packages
########################################
require(pacman)
p_load('tidyverse', 'jsonlite', 'magrittr', 'xlsx',
       'stargazer', 'psych', 'jtools', 'DT', 'ggstatsplot', 
       'lavaan', 
       'regsem', 'MplusAutomation', 'igraph')

########################################
# list data files
########################################
setwd("data")
folders <- list.files(pattern = "^study_result.*")

########################################
# create data files - GERMANY
########################################
### get CAM data
writeLines("", "CAMdata.txt") # create file
text_connection <- file("CAMdata.txt", "a") # open connection to append

### get pre CAM data
writeLines("", "preCAM.txt") # create file
text_connection_pre <- file("preCAM.txt", "a") # open connection to append

### get post CAM data
writeLines("", "postCAM.txt") # create file
text_connection_post <- file("postCAM.txt", "a") # open connection to append

for(i in 1:length(folders)){
  setwd(folders[i])
  if(length(dir()) == 3){
    # print(i)
    ### CAM data
    setwd(dir()[2])
    tmp <- jsonlite::fromJSON(txt = "data.txt")
    writeLines(jsonlite::toJSON(x = tmp), text_connection)
    setwd("..")

    ### pre CAM data
    setwd(dir()[1])
    tmp <- jsonlite::fromJSON(txt = "data.txt")
    writeLines(jsonlite::toJSON(x = tmp), text_connection_pre)
    setwd("..")

    ### post CAM data
    setwd(dir()[3])
    tmp <- jsonlite::fromJSON(txt = "data.txt")
    writeLines(jsonlite::toJSON(x = tmp), text_connection_post)
    setwd("..")
  }
  setwd("..")
}

close(text_connection) # close connection CAM
close(text_connection_pre) # close connection
close(text_connection_post) # close connection

########################################
# move files to output folder
########################################
### copy files (not overwritten)
tmp_file_from <-  getwd()
setwd("../outputs")
file.copy(from =  paste0(tmp_file_from, "/CAMdata.txt"), to = paste0(getwd(), "/CAMdata.txt"))
file.copy(from =  paste0(tmp_file_from, "/preCAM.txt"), to = paste0(getwd(), "/preCAM.txt"))
file.copy(from =  paste0(tmp_file_from, "/postCAM.txt"), to = paste0(getwd(), "/postCAM.txt"))

### remove files
file.remove(paste0(tmp_file_from, "/CAMdata.txt"))
file.remove(paste0(tmp_file_from, "/preCAM.txt"))
file.remove(paste0(tmp_file_from, "/postCAM.txt"))

########################################
# load functions
########################################
print(getwd())
setwd("../../../functions")
for(i in 1:length(dir())){
  # print(dir()[i])
  source(dir()[i], encoding = "utf-8")
}


setwd("../functions_CAMapp")
for(i in 1:length(dir())){
  # print(dir()[i])
  source(dir()[i], encoding = "utf-8")
}
rm(i)



# summary function
data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      se = sd(x[[col]], na.rm=TRUE) / sqrt(length(x[[col]])))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- plyr::rename(data_sum, c("mean" = varname))
  return(data_sum)
}
```

# Notes


# prepare data

## set up data.frame questionnaires


```{r}
setwd("outputs")
# > pre study
suppressMessages(read_file('preCAM.txt') %>%
                   # ... split it into lines ...
                   str_split('\n') %>% first() %>%
                   # ... filter empty rows ...
                   discard(function(x) x == '') %>%
                   discard(function(x) x == '\r') %>%
                   # ... parse JSON into a data.frame
                   map_dfr(fromJSON, flatten=TRUE)) -> dat_preCAM
# > post first CAM
read_file('postCAM.txt') %>%
                   # ... split it into lines ...
                   str_split('\n') %>% first() %>%
                   # ... filter empty rows ...
                   discard(function(x) x == '') %>%
                   discard(function(x) x == '\r') -> tmp_postCAM


tmp_out <- list()
for(i in 1:length(tmp_postCAM)){
tmp_out[[i]] <- fromJSON(tmp_postCAM[i])
tmp_out[[i]]$"21" <- NULL # causes error
}


dat_postCAM = dplyr::bind_rows(tmp_out)







########################################
# create counter variable for both data sets
########################################
### pre study
dat_preCAM$ID <- NA

tmp_IDcounter <- 0
for(i in 1:nrow(dat_preCAM)){
  if(!is.na(dat_preCAM$sender[i]) && dat_preCAM$sender[i] == "Greetings"){
    # tmp <- dat_preCAM$prolific_pid[i]
    tmp_IDcounter = tmp_IDcounter + 1
  }
  dat_preCAM$ID[i] <- tmp_IDcounter
}



### post study
dat_postCAM$ID <- NA

tmp_IDcounter <- 0
for(i in 1:nrow(dat_postCAM)){
  if(!is.na(dat_postCAM$sender[i]) && dat_postCAM$sender[i] == "CAMfeedbackGeneral"){
    # tmp <- dat_postCAM$prolific_pid[i]
    tmp_IDcounter = tmp_IDcounter + 1
  }
  dat_postCAM$ID[i] <- tmp_IDcounter
}



########################################
# keep only complete data sets
########################################
### pre-study
# sort(table(dat_preCAM$ID))
sum(table(dat_preCAM$ID) != max(table(dat_preCAM$ID)))
sum(table(dat_preCAM$ID) == max(table(dat_preCAM$ID)))

dat_preCAM <- dat_preCAM[dat_preCAM$ID %in% names(table(dat_preCAM$ID))[table(dat_preCAM$ID) == max(table(dat_preCAM$ID))],]

### post-study
# sort(table(dat_postCAM$ID))
sum(table(dat_postCAM$ID) != max(table(dat_postCAM$ID)))
sum(table(dat_postCAM$ID) == max(table(dat_postCAM$ID)))


dat_postCAM <- dat_postCAM[dat_postCAM$ID %in% names(table(dat_postCAM$ID))[table(dat_postCAM$ID) == max(table(dat_postCAM$ID))],]



########################################
# json (from JATOS) to 2D data.frame
########################################
################################ pre-study
### add paradata
tmp_notNumeric <- str_subset(string = colnames(dat_preCAM), pattern = "^meta|^R")
tmp_notNumeric <- str_subset(string = tmp_notNumeric, pattern = "labjs|location", negate = TRUE)

### get survey
vec_ques <- c("PROLIFIC_PID",
              "dummy_informedconsent", 
              "commCheck",
              tmp_notNumeric)

vec_notNumeric = c("PROLIFIC_PID", tmp_notNumeric)

questionnaire_preCAM <- questionnairetype(dataset = dat_preCAM, 
                                        listvars = vec_ques, 
                                        notNumeric = vec_notNumeric, verbose = FALSE)


dim(questionnaire_preCAM)



################################ post-study
tmp_numeric <- str_subset(string = colnames(dat_postCAM), pattern = "^nfc")


vec_ques <- c("PROLIFIC_PID", "commCheck",
              "feedCAM_repres", "feedCAM_technicalprobs", "feedCAM_technicalprobsText", "feedCAM_already","feedCAM_alreadyText",
              "openQuestion_MaterialSystem",
              "openQuestion_Ethic",
              "openQuestion_missedPositive", "openQuestion_missedNegative",
              "outcome_research", "outcome_prohibition", "outcome_buy", "outcome_buy_text", 
              "education", "experienceMS",
              tmp_numeric,
              "feedback_critic")

     

vec_notNumeric = c("PROLIFIC_PID", 
                   "feedCAM_technicalprobsText", "feedCAM_alreadyText", 
                                 "openQuestion_MaterialSystem",
                                 "openQuestion_Ethic",
              "openQuestion_missedPositive", "openQuestion_missedNegative",
   "outcome_research", "outcome_prohibition", "outcome_buy", "outcome_buy_text", 
                   "education", "experienceMS",
                   "feedback_critic")

questionnaire_postCAM <- questionnairetype(dataset = dat_postCAM,
                                        listvars = vec_ques,
                                        notNumeric = vec_notNumeric, verbose = FALSE)

questionnaire_postCAM$feedback_critic[questionnaire_postCAM$feedback_critic == ""] <- NA
dim(questionnaire_postCAM)


questionnaire_postCAM$multipleEthic <- NA
tmp_multipleEthic <- cbind(dat_postCAM$ID, dat_postCAM$multipleEthic)

questionnaire_postCAM$multiplePositive <- NA
tmp_multiplePositive <- cbind(dat_postCAM$ID, dat_postCAM$multiplePositive)

questionnaire_postCAM$multipleNegative <- NA
tmp_multipleNegative <- cbind(dat_postCAM$ID, dat_postCAM$multipleNegative)


for(i in questionnaire_postCAM$ID){
  # add multipleEthic
  tmp <- tmp_multipleEthic[tmp_multipleEthic[,1] == i, ]
  if(length(unlist(tmp[,2])) == 3){
    questionnaire_postCAM$multipleEthic[questionnaire_postCAM$ID == i] <- paste0(unlist(tmp[,2]), collapse = " \\ ")
  }
  
  # add multiplePositive
    tmp <- tmp_multiplePositive[tmp_multiplePositive[,1] == i, ]
  if(length(unlist(tmp[,2])) == 3){
    questionnaire_postCAM$multiplePositive[questionnaire_postCAM$ID == i] <- paste0(unlist(tmp[,2]), collapse = " \\ ")
  }
    
      # add multipleNegative
    tmp <- tmp_multipleNegative[tmp_multipleNegative[,1] == i, ]
  if(length(unlist(tmp[,2])) == 3){
    questionnaire_postCAM$multipleNegative[questionnaire_postCAM$ID == i] <- paste0(unlist(tmp[,2]), collapse = " \\ ")
  }
}


dim(questionnaire_postCAM)



################################ merge two data sets
questionnaire_postCAM$ID <- NULL
questionnaire <- left_join(questionnaire_preCAM, questionnaire_postCAM, by="PROLIFIC_PID")
dim(questionnaire)
```



## set up CAM data

### pre

Load CAM data

```{r, message = FALSE}
setwd("outputs")
suppressMessages(read_file("CAMdata.txt") %>%
  # ... split it into lines ...
  str_split('\n') %>% first() %>%
    discard(function(x) x == '') %>%
    discard(function(x) x == '\r') %>%
  # ... filter empty rows ...
  discard(function(x) x == '')) -> dat_CAM_pre

raw_CAM <- list()
for(i in 1:length(dat_CAM_pre)){
  raw_CAM[[i]] <- jsonlite::fromJSON(txt = dat_CAM_pre[[i]])
}
```

Create CAM files, draw CAMs and compute network indicators

```{r, message = FALSE}
########################################
# create CAM single files (nodes, connectors, merged)
########################################
CAMfiles <- create_CAMfiles(datCAM = raw_CAM, reDeleted = TRUE)
## remove white spaces within pre-defined concepts
CAMfiles[[1]]$text <- str_replace_all(string = CAMfiles[[1]]$text, "\\s+", " ")
CAMfiles[[1]]$text <- str_trim(string = CAMfiles[[1]]$text, side = "both")


########################################
# draw CAMs
########################################
CAMdrawn <- draw_CAM(dat_merged = CAMfiles[[3]],
                     dat_nodes = CAMfiles[[1]],ids_CAMs = "all",
                     plot_CAM = FALSE,
                     useCoordinates = TRUE,
                     relvertexsize = 3,
                     reledgesize = 1)


########################################
# draw CAMs
########################################
tmp_microIndicator <- V(CAMdrawn[[1]])$label # all concepts are pre-defined
networkIndicators <- compute_indicatorsCAM(drawn_CAM = CAMdrawn, 
                                           micro_degree = tmp_microIndicator, 
                                           micro_valence = tmp_microIndicator, 
                                           micro_centr_clo = tmp_microIndicator, 
                                           micro_transitivity = tmp_microIndicator, 
                                           largestClique = FALSE)


########################################
# wordlists
########################################
CAMwordlist <- create_wordlist(
  dat_nodes =  CAMfiles[[1]],
  dat_merged =  CAMfiles[[3]],
  order = "alphabetic",
  splitByValence = FALSE,
  comments = TRUE,
  raterSubsetWords = NULL,
  rater = FALSE
)

DT::datatable(CAMwordlist, options = list(pageLength = 5)) 
```

### plot CAMs using igraph package

Just plot first 10 CAMs for an impression

```{r}
for(i in 1:10){ # length(CAMdrawn)
  plot(CAMdrawn[[i]], edge.arrow.size = .7,
       layout=layout_nicely, vertex.frame.color="black", asp = .5, margin = -0.1,
       vertex.size = 10, vertex.label.cex = .9)
}
```


### plot aggregated CAM

```{r}

sel_ids <- unique(CAMfiles[[1]]$participantCAM)
CAMaggregated <- aggregate_CAMs(dat_merged = CAMfiles[[3]], dat_nodes = CAMfiles[[1]],
                                ids_CAMs = sel_ids)

# plot(CAMaggregated[[2]], vertex.size=diag(CAMaggregated[[1]]) / max(diag(CAMaggregated[[1]]))*20, edge.arrow.size=0.01)
# plot(CAMaggregated[[2]], vertex.size=(abs(V(CAMaggregated[[2]])$value)+1)*5, edge.arrow.size=0.01)


g = CAMaggregated[[2]]
g2 = simplify(CAMaggregated[[2]])
# plot(g2, edge.arrow.size=0.01,
#      vertex.size=diag(CAMaggregated[[1]]) / max(diag(CAMaggregated[[1]]))*20)

E(g2)$weight = sapply(E(g2), function(e) {
  length(all_shortest_paths(g, from=ends(g2, e)[1], to=ends(g2, e)[2])$res) } )
E(g2)$weight = E(g2)$weight * 2
# E(g2)$weight[E(g2)$weight == 1] <- NA

V(g2)$color[V(g2)$value <= .5 & V(g2)$value >= -.5] <- "yellow"

V(g2)$shape <- NA
V(g2)$shape <- ifelse(test = V(g2)$color == "yellow", yes = "square", no = "circle")



### > plot multiple times because of random layout
for(i in 1:3){
  plot(g2, edge.arrow.size = 0,
     layout=layout_nicely, vertex.frame.color="black", asp = .5, margin = -0.1,
     vertex.size=diag(CAMaggregated[[1]]) / max(diag(CAMaggregated[[1]]))*5,
     vertex.label.cex = .9, 
     edge.weight=2, edge.width=(E(g2)$weight/3))
}
```


### save CAMs as .json files, and as .png (igraph)


```{r saveCAMs_pictures_pre, message = FALSE}
save_CAMs_as_pictures = TRUE

if(save_CAMs_as_pictures){
  setwd("outputs")

setwd("savedCAMs")
setwd("png")
### remove all files if there are any
if(length(list.files()) >= 1){
  file.remove(list.files())
  cat('\n!
      all former .png files have been deleted')
}

### if no participant ID was provided replace by randomly generated CAM ID

if(all(CAMfiles[[3]]$participantCAM.x == "noID")){
  CAMfiles[[3]]$participantCAM.x <- CAMfiles[[3]]$CAM.x
}

### save as .json files, and as .png (igraph)
ids_CAMs <- unique(CAMfiles[[3]]$participantCAM.x); length(ids_CAMs)


for(i in 1:length(ids_CAMs)){
  save_graphic(filename = paste0(ids_CAMs[i]))
  CAM_igraph <- CAMdrawn[[c(1:length(CAMdrawn))[
    names(CAMdrawn) == paste0(unique(CAMfiles[[3]]$participantCAM.x)[i])]]]
  plot(CAM_igraph, edge.arrow.size = .7,
       layout=layout_nicely, vertex.frame.color="black", asp = .5, margin = -0.1,
       vertex.size = 10, vertex.label.cex = .9)
  dev.off()
}

setwd("../json")
### remove all files if there are any
if(length(list.files()) >= 1){
  file.remove(list.files())
  cat('\n!
      all former .json files have been deleted')
}
for(i in 1:length(raw_CAM)){
  if(!is_empty(raw_CAM[[i]]$nodes)){
    if(nrow(raw_CAM[[i]]$nodes) > 5){
      write(toJSON(raw_CAM[[i]], encoding = "UTF-8"),
            paste0(raw_CAM[[i]]$idCAM, ".json"))
    }
  }
}
}
```


# analyze data

## describe data set

### feedback to the study

Question: 

```{r}
DT::datatable(questionnaire[,c("PROLIFIC_PID", "feedback_critic")], options = list(pageLength = 5)) 
```

### Material system that has been thought of

Question:  Bitte beschreiben Sie an an welches Materialsystem oder welche Materialsysteme Sie dabei gedacht haben. 

```{r}
DT::datatable(questionnaire[,c("PROLIFIC_PID", "openQuestion_MaterialSystem")], options = list(pageLength = 5)) 
```

### basal attributes: most pos. / neg.

Question: Welche drei Begriffen nehmen Sie am positivsten bzw. negativsten für die Beschreibung neuer Materialsysteme wahr?


```{r}
## most positive
tmp <- str_trim(unlist(str_split(string = questionnaire$multiplePositive, pattern = "\\\\")))
sort(table(tmp))

## most negative
tmp <- str_trim(unlist(str_split(string = questionnaire$multipleNegative, pattern = "\\\\")))
sort(table(tmp))

## answers of participants
DT::datatable(questionnaire[,c("PROLIFIC_PID", "multiplePositive", "multipleNegative")], options = list(pageLength = 5)) 
```


**any basal attributes missing?**

Question:  Fallen Ihnen weitere Eigenschaften ein, die Sie als relevant oder negativ für die Beschreibung neuer Materialsysteme erachten, die in der Liste nicht aufgeführt sind, so können Sie diese gerne in folgenden Textfeldern ergänzen: 


```{r}
## answers of participants
DT::datatable(questionnaire[,c("PROLIFIC_PID", "openQuestion_missedPositive", "openQuestion_missedNegative")], options = list(pageLength = 5)) 
```



### basal attributes: ethical most relevant

Question:  Welche drei Begriffe sind aus Ihrer Sicht in moralischer Hinsicht am "relevantesten"?


```{r}
## ethical relevant
tmp <- str_trim(unlist(str_split(string = questionnaire$multipleEthic, pattern = "\\\\")))
sort(table(tmp))

## answers of participants
DT::datatable(questionnaire[,c("PROLIFIC_PID", "multipleEthic")], options = list(pageLength = 5)) 
```

**argument for choosen basal attributes**

Question: Bitte begründen Sie kurz die Auswahl der ethisch relevanten Begriffe:


```{r}
## answers of participants
DT::datatable(questionnaire[,c("PROLIFIC_PID", "openQuestion_Ethic")], options = list(pageLength = 5)) 
```


### outcome questions

Question: Sollte die Entwicklung innovativer Materialsysteme mit öffentlichen Mitteln gefördert werden? 	

```{r}
table(questionnaire$outcome_research)
```

Question: Sollten die Erforschung und Entwicklung solcher innovativer Materialsysteme verboten werden?

```{r}
table(questionnaire$outcome_prohibition)
```

Question: Wären Sie bereit, Produkte zu kaufen, die innovative Materialsysteme enthalten? 


```{r}
table(questionnaire$outcome_buy)
```

> if yes to previous question

Question: An welche möglichen Produkte haben Sie gedacht? 

```{r}
## answers of participants
DT::datatable(questionnaire[,c("PROLIFIC_PID", "outcome_buy_text")], options = list(pageLength = 5)) 
```

 	
## co-variation of basal attributes

Compare the probability that two concepts are connected in randomly generated networks to drawn CAMs:

```{r}
## get average number of drawn concepts (here fixed)
numConcepts <- mean(networkIndicators$num_nodes_macro)
## get average density
numDensity <- mean(networkIndicators$density_macro)

## simply get the average probability that two concepts are connected:
g <- igraph::random.graph.game(n = numConcepts, p.or.m = numDensity)
plot(g)
are.connected(g, 1, 2)


#> whereby each edge to be drawn has the identical probability in the Erdős–Rényi model
vec_booleanConnected <- c()
# vec_booleanConnected2 <- c()

for(i in 1:10000){
  g <- igraph::random.graph.game(n = numConcepts, p.or.m = numDensity)
  vec_booleanConnected[i] <- are.connected(g, 1, 2)
    # vec_booleanConnected2[i] <- are.connected(g, 22, 26)
}
baselineProbability <- mean(vec_booleanConnected)
baselineProbability
# mean(vec_booleanConnected2)
```

This baseline probability can be compared to all possible combinations of drawn concepts: 

```{r}
vec_boolean <- c()
for(i in 1:length(CAMdrawn)){
  vec_boolean[i] <- are.connected(graph = CAMdrawn[[i]], 
              v1 = V(CAMdrawn[[i]])[V(CAMdrawn[[i]])$label == "robust"], 
              v2 = V(CAMdrawn[[i]])[V(CAMdrawn[[i]])$label == "widerstandsfähig"])
}

mean(vec_boolean)
```


